Notes on Control Plane Inference

### 2021-03-27 inference.tex
partially fix scoping issue, still need to generalize pop-up rule

% Theorems
\newtheorem{theorem}{Theorem}

@@

For actions, we restrict the language to be generated by only assignment, assumption, assertion and sequence, excluding table application and nondeterministic choice.

@@

@@

A state map $\sigma : \Value \to \Row^*$ is well-formed for a command $c$ iff the
following conditions hold:
\begin{enumerate}
\item[\textsc{WellFormedRows}] For every $t\in \tables(c)$, every row in $\sigma(t.\id)$ is well-formed.
\item[\textsc{NoShadow}] For every $t \in \tables(c)$, with $r_1,\ldots,r_n =
  \sigma(t.\id)$, for every $1 \leq i \leq n$, there does not exist $1 \leq j <
  i$ such that $r_i.\matches = r_j.\matches$.
\end{enumerate}
\todo[inline]{Tables(c) is undefined}

\paragraph{Row Models}
We also need models $\mu \in \Model$ to indicate which symbolic rows corresponds
to which concrete rows, i.e. $\Model = \SymbRow \rightharpoonup \Row$. We write
$\mu\{\rho \mapsto r\}$ to extend $\mu$ by mapping $\rho$ to $r$, and write $\mu
\setminus \rho$, to remove $\rho$ from the map.

@@

@@

      \\\\
      (\textrm{by \textsc{Hit}, \textsc{NoShadow}, and the definition of }\denote{-}) \\
      \\
      = \bigcup_{i=0}^{|t.\action| -1}\denote{
       \begin{array}{l}
          \assume \rho.\action = i;\\
          t.\actions[i](\rho.\data)
      \end{array}}^\sigma~(\mu\{\rho \mapsto r_i\})~\pkt \\
      = \bigcup_{j=0}^{|t.\action| -1}\denote{
       \begin{array}{l}
          \assume r_i.\action = j;\\
          t.\actions[j](r_i.\data)
      \end{array}}^\sigma~(\mu\{\rho \mapsto r_i\})~\pkt \\
      \textrm{\textcolor{red}{TODO LEMMA}} \\
      = \denote{t.\actions[r_i.\action](r_i.\data)}^\sigma~(\mu\{\rho \mapsto r_i\})~\pkt \\
      = \denote{c[r_i.\data/\vec x]}^\sigma~(\mu\{\rho \mapsto r_i\})~\pkt
      \end{array}\]

      Since $\rho$ is fresh in $c$, and consequently in $c[r_i.\data/\vec x]$,
      then by \textcolor{red}{Lemma},
      \[\{(\mu'\setminus \rho,\pkt')
      \mid (\mu', \pkt') \in \denote{c[r_i.\data/\vec x]}^\sigma~(\mu\{\rho \mapsto r_i\})~\pkt\}
       = \denote{c[r_i.\data/\vec x]}^\sigma~\mu~\pkt
       \]
       \todo[inline]{Relies on the fact that $\rho \not \in \mu$, or that $\rho$ is globally fresh}

>>>>

% Theorems
\newtheorem{theorem}{Theorem}
\newtheorem{lemma}{Lemma}

@@

@@

For actions, we restrict the language to be generated by only non-symbolic
assignment, sequence, and $\SKIP$.

@@

A state map $\sigma : \Value \to \Row^*$ is well-formed for a command $c$ iff the
following conditions hold:
\begin{enumerate}
\item[\textsc{WellFormedRows}] For every $t\in \tables(c)$, every row in $\sigma(t.\id)$ is well-formed.
\item[\textsc{NoShadow}] For every $t \in \tables(c)$, with $r_1,\ldots,r_n =
  \sigma(t.\id)$, for every $1 \leq i \leq n$, there does not exist $1 \leq j <
  i$ such that $r_i.\matches = r_j.\matches$.
\end{enumerate}
\paragraph{Row Models}
We also need models $\mu \in \Model$ to indicate which symbolic rows corresponds
to which concrete rows, i.e. $\Model = \SymbRow \rightharpoonup \Row$. We write
$\mu\{\rho \mapsto r\}$ to extend $\mu$ by mapping $\rho$ to $r$, and write $\mu
\setminus \rho$, to remove $\rho$ from the map.

@@

\begin{lemma}[Models Invariant over Actions]
  \label{lem:models-invariant-over-actions}
  For an action command $c$, $\mu,\mu'
  \in \Model$, $\sigma \in \Value \to
  \Row^*$, $\pkt \in \Pkt$, there exists some $\pkt'$
  \[\denote{c}^\sigma\,\mu\,\pkt = \{\mu,\pkt'\}\]
  \end{lemma}

\begin{proof}
  Proceed by induction over $c$.
  \begin{enumerate}[align=left]
  \item[($c = \SKIP$)] Immediate.
  \item[$(c = h.f = e)$] Immediate.
  \item[$(c = c_1;c_2)$]
    By IH($c_1$) there exists some $\pkt''$ such that
    $\denote{c_1}^\sigma\,\mu\,\pkt = \{(\mu,\pkt'')\}$.
    By IH($c_2$) there exists some $\pkt'$ such that
    $\denote{c_2}^\sigma,\mu\,pkt'' = \{(\mu, \pkt')\}$.
    The result follows by definition of $\denote{-}$.
    \end{enumerate}
\end{proof}

@@

      \\\\
      (\textrm{by \textsc{Hit}, \textsc{NoShadow}, and the definition of }\denote{-}) \\
      \\
      = \bigcup_{i=0}^{|t.\action| -1}\denote{
       \begin{array}{l}
          \assume \rho.\action = i;\\
          t.\actions[i](\rho.\data)
      \end{array}}^\sigma~(\mu\{\rho \mapsto r_i\})~\pkt \\
      = \bigcup_{j=0}^{|t.\action| -1}\denote{
       \begin{array}{l}
          \assume r_i.\action = j;\\
          t.\actions[j](r_i.\data)
      \end{array}}^\sigma~(\mu\{\rho \mapsto r_i\})~\pkt \\
      \textrm{\textcolor{red}{TODO LEMMA}} \\
      = \denote{t.\actions[r_i.\action](r_i.\data)}^\sigma~(\mu\{\rho \mapsto r_i\})~\pkt \\
      = \denote{c[r_i.\data/\vec x]}^\sigma~(\mu\{\rho \mapsto r_i\})~\pkt \\
      \end{array}\]

      By Lemma~\ref{lem:models-invariant-over-actions}, there's some $\pkt'$ such that
      \[\{\mu\{\rho \mapsto r_i\}, \pkt'\} =
      \denote{c[r_i.\data/\vec x]}^\sigma~(\mu\{\rho \mapsto r_i\})~\pkt
      \]

      which means that the result of the first branch is
      \[\{\mu, \pkt'\} =
      \denote{c[r_i.\data/\vec x]}^\sigma~(\mu\{\rho \mapsto r_i\})~\pkt
      \]

      Since $\rho$ doesn't occur in $c$, then also
      \[\{\mu, \pkt'\} = \denote{c[r_i.\data/\vec x]}^\sigma~\mu~\pkt \]
